Performance Optimization of Service Chain \\ for vCPE in Small Size Network \\ with OpenFlow Switch

### 2017-03-02 netsoft_paper.tex
fix some style
fix picture

\usepackage{indentfirst}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{subfigure}
\usepackage{enumerate}
\usepackage{epstopdf}
\usepackage{csquotes}
\usepackage{hyperref}
\usepackage{cite}
\usepackage{url}
\usepackage{amsmath}
\usepackage[flushleft]{threeparttable}
\usepackage[super]{nth}

\graphicspath{{figures/}}

@@

\IEEEauthorblockA{
\IEEEauthorrefmark{1}
Department of Computer Science National Tsing Hua University, Hsinchu, Taiwan}
\IEEEauthorblockA{
\IEEEauthorrefmark{2}
Institute of Communication Engineering National Tsing Hua University, Hsinchu, Taiwan}
}

@@

\subsection{Architecture of the vCPE System}
The architecture of the vCPE system is adapted from \cite{nfv2014-v111}, shown in Fig. \ref{fig:desc_vcpe_framework}, including of a Infrastructure Controller, Infrastructure Orchestrator, Cloud Database, VNF Controllers and VNF Orchestrator.
The Infrastructure Orchestrator, VNF Orchestrator and Cloud Database are web servers
Each component is introduced in the subsection below.

\begin{figure}[!t]
\centering
\includegraphics[width=3in]{./figures/desc_vcpe_framework}
\caption{Architecture of the vCPE framework.}
\label{fig:desc_vcpe_framework}
\end{figure}

@@

\newpage
\bibliographystyle{ieeetr}
\bibliography{paper}

>>>>

\usepackage{graphicx}
\usepackage{indentfirst}
\usepackage{cite}
\usepackage{url}
\usepackage{hyperref}
\usepackage{amsmath}
\usepackage{fixltx2e}
\usepackage{caption}
\usepackage{enumerate}
\usepackage[flushleft]{threeparttable}
\usepackage[super]{nth}

@@

\IEEEauthorblockA{
\IEEEauthorrefmark{1}
Department of Computer Science National Tsing Hua University, Hsinchu, Taiwan} \\
\IEEEauthorblockA{
\IEEEauthorrefmark{2}
Institute of Communication Engineering National Tsing Hua University, Hsinchu, Taiwan}
}

@@

\subsection{Architecture of the vCPE System}
The architecture of the vCPE system is adapted from the NFV-MANO architectural framework in \cite{nfv2014-v111}, shown in Fig. \ref{fig:desc_vcpe_framework}, including of a Infrastructure Controller, Infrastructure Orchestrator, Cloud Database, VNF Controllers and VNF Orchestrator.
The Infrastructure Orchestrator, VNF Orchestrator and Cloud Database are web servers
Each component is introduced in the subsection below.

\begin{figure}[!t]
\centering
\includegraphics[width=3.5in]{./figures/desc_vcpe_framework}
\caption{Architecture of the vCPE framework.}
\label{fig:desc_vcpe_framework}
\end{figure}

@@

\bibliographystyle{ieeetr}
\bibliography{paper}
